---
title: "Varying thresholds for poverty mapping"
output: pdf_document
bibliography: lit_examples.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Poverty mapping with emdi based on the empirical best prediction 

The ebp function in package emdi returns ten different indicators by default. These
include the head count ratio and the poverty gap. Both indicators makes use of
a threshold or a poverty line. This threshold could be a fixed value or based on 
the indicator of interst, e.g., 60% of the median income. In the latter case, the 
poverty line needs to be calculated in each bootstrap iteration for the estimation 
of the uncertainty measure. Thus, it should be given as a function to the threshold 
argument in the ebp function. 

### Load package and data

The emdi package loaded here is the emdi package published on [CRAN](https://cran.r-project.org/web/packages/emdi/index.html). The installation 
is explained in installEmdiExtensions.

For the data, unit-level survey and population data is loaded.

```{r loadData}
# Load package
library(emdi)

# Load aggregated data
data("eusilcA_pop")
data("eusilcA_smp")
```


### One fixed poverty line

One way to add a poverty line is a fixed value. This could be, e.g., 10885.33. 

For an application, the bootstrap iterations should be increased but due to 
computational reasons B is set to 2.

```{r fixedLine}
emdi_model <- ebp(fixed = eqIncome ~ gender + eqsize + cash + self_empl + 
                    unempl_ben + age_ben + surv_ben + sick_ben + dis_ben + rent +
                    fam_allow + house_allow + cap_inv + tax_adj, pop_data = eusilcA_pop,
                  pop_domains = "district", smp_data = eusilcA_smp,
                  smp_domains = "district", threshold = 10885.33, MSE = TRUE, 
                  B = 2)
head(estimators(emdi_model))
```

### Poverty line as a function of y

Another way to add a poverty line is a function of y.  For instance, the EU countries
use 60% of the median equvalized disposable income. In emdi, a function of y that 
calculates 60% of the median of y could be used as a threshold. This also enables the 
calculation of a poverty line in each bootstrap iteration for the uncertainty measure.  

For an application, the bootstrap iterations should be increased but due to 
computational reasons B is set to 2.

```{r function}
emdi_model <- ebp(fixed = eqIncome ~ gender + eqsize + cash + self_empl + 
                    unempl_ben + age_ben + surv_ben + sick_ben + dis_ben + rent +
                    fam_allow + house_allow + cap_inv + tax_adj, pop_data = eusilcA_pop,
                  pop_domains = "district", smp_data = eusilcA_smp,
                  smp_domains = "district", threshold = function(y){0.6 * median(y)},
                  MSE = TRUE, B = 2)
head(estimators(emdi_model))
```

### Mixed indicator based on two poverty lines

In some applications, it is of interest to use different poverty lines for, e.g., 
rural and urban areas. Since it is only possible to add one poverty line to 
function ebp, following workaround is possible. 

In the following, two poverty lines 10885.33 and 8885.33 are used to estimate 
two head count ratios using the two poverty lines, respectively. The first one 
is the automatically returned head count ratio. The second will be defined 
as a custom indicator which will be the future mixed indicator.

```{r twoLines}
emdi_model <- ebp(fixed = eqIncome ~ gender + eqsize + cash + self_empl + 
                    unempl_ben + age_ben + surv_ben + sick_ben + dis_ben + rent +
                    fam_allow + house_allow + cap_inv + tax_adj, pop_data = eusilcA_pop,
                  pop_domains = "district", smp_data = eusilcA_smp,
                  smp_domains = "district", threshold = 10885.33,
                  MSE = TRUE, B = 2, 
                  custom_indicator = list(mixed_hcr = function(y, threshold){mean(y < 8885.33)}))
head(estimators(emdi_model))
```

This emdi_model object returns the Head_Count with the poverty line 10885.33 and
the mixed_hcr with the poverty line 8885.33. Assuming, that the poverty line 
10885.33 applies to the first 20 domains and the poverty line 8885.33 otherwise, 
the mixed_hcr indicator can be updated as follows. 

```{r manipulation}
first20 <- rep(FALSE, 94)
first20[1:20] <- TRUE 

emdi_model$ind$mixed_hcr[first20] <- emdi_model$ind$Head_Count[first20]
emdi_model$MSE$mixed_hcr[first20] <- emdi_model$MSE$Head_Count[first20]
head(estimators(emdi_model))
tail(estimators(emdi_model))
```

All methods can be applied on this manipulated emdi_model object. 

```{r mapping}
load_shapeaustria()
map_plot(emdi_model, indicator = c("Head_Count", "mixed_hcr"), 
                                   map_obj = shape_austria_dis, map_dom_id = "PB", 
         scale_points = c(0, 0.6))
```






