---
title: "Spatial Fay-Herriot model"
output: pdf_document
bibliography: lit_examples.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Fay-Herriot (FH) estimator with spatially correlated random area effects

One extension of the Fay-Herriot model is the estimation of small area indirect 
estimators under area level random effect models when only area level data are 
available and the random effects are correlated [@pratesi2008].

### Load package and data

The emdi package loaded here is the one under development with the new area-level 
models. The installation is explained in installEmdiExtensions.

For the data, aggregted survey and population data is loaded and combined with 
function combined_data such that the indicators of interest (direct point and 
variance estimate) and the additional information are in one data frame.

```{r loadEssentials}
# Load package emdi
library(emdi)

# Load aggregated data
data("eusilcA_popAgg")
data("eusilcA_smpAgg")

# Combine sample and population data
combined_data <- combine_data(pop_data = eusilcA_popAgg, pop_domains = "Domain",
                             smp_data = eusilcA_smpAgg, smp_domains = "Domain")
head(combined_data)
```

### Create a spatial correlation matrix

For the estimation of the Fay-Herriot model with spatially correlated random 
effects, a spatial correlation matrix needs to be calculated. This matrix is 
one argument in the fh function.

The spatial correlation matrix can be calculated based on a shape file and with 
the help of functions from package maptools and spdep. 

```{r createSpatialCorrelationMatrix, warning = FALSE}
library(maptools)
library(spdep)

# Load shapefile
load_shapeaustria()
austria_shape <- merge(shape_austria_dis, eusilcA_smpAgg, by.x = "PB",
                       by.y = "Domain", all.x = F)
rel <- poly2nb(austria_shape, row.names = austria_shape$PB)
euSilcA_prox <- nb2mat(rel, style = "W", zero.policy = TRUE)
head(euSilcA_prox)
```

### Estimate the FH estimates with spatially correlated random area effects

In the following, the various options for adding spatially correlated random 
area effects in package emdi are presented: correlation = "spatial". 

#### Standard

One way to add spatially correlated random area effects follows @pratesi2008. In
this specification, following estimation methods are possible:

* Variance estimation: 
    + Maximum likelihood (method = "ml")
    + Restricted maximum likelihood (method = "reml")
* MSE estimation: 
    + Analytical (default, mse_type = "analytical")
    + Naive parametric bootstrap (mse_type = "spatialparboot")
    + Bias corrected parametric bootstrap (mse_type = "spatialparbootbc")
    + Naive nonparametric bootstrap (mse_type = "spatialnonparboot")
    + Bias corrected nonparametric bootstrap (mse_type = "spatialnonparbootbc")

```{r fitSpatialFH}
fh_spatial <- fh(fixed = Mean ~ cash + self_empl, vardir = "Var_Mean", 
                 tol = 0.00000001, maxit = 2000, combined_data = combined_data, 
                 domains = "Domain", method = "reml", correlation = "spatial", 
                 corMatrix = eusilcA_proxmat, MSE = TRUE)
fh_spatial
```

#### Robust

The package also offers a robust estimation of the FH model with spatially 
correlated random area effects following @Warnholz2016c. In this specification, 
following estimation methods are possible: 

```{r fitRobustSpatialFH}
fh_robustSpatial <- fh(fixed = Mean ~ cash + self_empl, vardir = "Var_Mean", 
                 tol = 0.00000001, maxit = 2000, combined_data = combined_data, 
                 domains = "Domain", method = "reblupbc", correlation = "spatial", 
                 corMatrix = eusilcA_proxmat, MSE = TRUE, mse_type = "boot", B = 2)
fh_robustSpatial
```



