---
title: "Spatial Fay-Herriot model"
output: pdf_document
bibliography: lit_examples.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Fay-Herriot estimator with spatially correlated random area effects

One extension of the Fay-Herriot model is the estimation of small area indirect 
estimators under area level random effect models when only area level data are 
available and the random effects are correlated [@pratesi2008].

```{r spatialInitial}
library(emdi)
fh_spatial <- fh(fixed = Mean ~ cash + self_empl, vardir = "Var_Mean", 
tol = 0.00000001, maxit = 2000, combined_data = combined_data, 
domains = "Domain", method = "reml", correlation = "spatial", 
corMatrix = eusilcA_proxmat, MSE = TRUE, mse_type = "analytical")
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
