---
title: "Install the extension of package emdi from second branch"
output: pdf_document
bibliography: lit_examples.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Package emdi 1.1.7

Package emdi contains functions that support estimating, assessing and mapping 
regional disaggregated indicators. In the first version, estimation methods 
comprised direct estimation and the model-based approach Empirical Best Prediction 
[@Molina2010] as well as their precision estimates.

The package is available on [CRAN](https://cran.r-project.org/web/packages/emdi/index.html) and a corresponding article is published in the Journal of Statistical Software [@Kreutzmann2019].

```{r emdi1.0, eval = FALSE}
install.packages("emdi")
library(emdi)
```


## Planned developments: Integration of area-level models

Currently, major extension are added to the package: various area-level models. 
These will be added to the original package but so far, these are available via 
[github](https://github.com/SoerenPannier/emdi). The installation may require 
the manual installation of dependencies. 


```{r emdi2.0, eval = FALSE}
library(githubinstall)
gh_install_packages("emdi", ref = "fh_integration")
```

## References

